Initial Analysis

### 2020-07-31 Scripts/Initial_Analysis.Rmd
updated statistics

summary(mano)
# Df  Pillai approx F num Df den Df    Pr(>F)    
# observation   2 0.21621   27.091      4    894 < 2.2e-16 ***
# Residuals   447

summary.aov(mano)
#  Response Discrete_value :
#              Df Sum Sq Mean Sq F value    Pr(>F)    
# observation   2   7088  3544.1  26.305 1.584e-11 ***
# Residuals   447  60226   134.7                      
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
#  Response Trans_value :
#              Df Sum Sq Mean Sq F value    Pr(>F)    
# observation   2  22778 11389.2  55.005 < 2.2e-16 ***
# Residuals   447  92555   207.1

@@

@@

@@

>>>>

summary(mano)
# Df  Pillai approx F num Df den Df    Pr(>F)    
# observation   2 0.21621   27.091      4    894 < 2.2e-16 ***
# Residuals   447
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
#  Response Trans_value :
#              Df Sum Sq Mean Sq F value    Pr(>F)    
# observation   2  22778 11389.2  55.005 < 2.2e-16 ***
# Residuals   447  92555   207.1

@@

     # Df Sum Sq Mean Sq F value Pr(>F)    
# observation   2  24776   12388   53.93 <2e-16 ***
# Residuals   459 105436     230

@@

#    diff       lwr      upr     p adj
# Category B-Category A  5.948052  1.886814 10.00929 0.0018096
# Category C-Category A 17.629870 13.568633 21.69111 0.0000000
# Category C-Category B 11.681818  7.620581 15.74306 0.0000000

@@

# f Sum Sq Mean Sq F value   Pr(>F)    
# observation   2   5322    2661   25.58 3.76e-11 ***
# Residuals   382  39740     104
